The \dealii{} Library, Version 9.2

### 2020-07-02 9.2/paper.tex
9.2 revision without DoE statement

\footnotetext{%
  $^\ast$ This manuscript has been authored by UT-Battelle, LLC under Contract No.
  DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
  Government retains and the publisher, by accepting the article for
  publication, acknowledges that the United States Government retains a
  non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
  the published form of this manuscript, or allow others to do so, for United
  States Government purposes. The Department of Energy will provide public
  access to these results of federally sponsored research in accordance with the
  DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}

>>>>

\footnotetext{%
  $^\ast$ This manuscript has been authored by UT-Battelle, LLC under Contract No.
  DE-AC05-00OR22725 with the U.S. Department of Energy.
  %The United States
  %Government retains and the publisher, by accepting the article for
  %publication, acknowledges that the United States Government retains a
  %non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
  %the published form of this manuscript, or allow others to do so, for United
  %States Government purposes. The Department of Energy will provide public
  %access to these results of federally sponsored research in accordance with the
  %DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).
}
